---
title: "Example to illustrate question on CrossValidated"
author: "Knut Anders Hovstad"
date: "2023-11-04"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
This is an example to illustrate a question asked on CrossValidated: 
https://stats.stackexchange.com/questions/630188/estimated-means-for-groups-based-on-continous-predictor-in-gamm?noredirect=1#comment1176408_630188

The objective is to describe offspring survival as a function of 
age of the mother. This species can only reproduce once a year so 
we are only interested in estimating probability of survival at 
integer values of the predictor age.

The data used in this example are not the actual data from the study
as I do not have the opportunity to share those at this stage. 


```{r message=FALSE}
library(tidyverse)
library(mgcv)
library(emmeans)
```

```{r message=FALSE}
example <- read_csv("example.csv")
```

```{r}
m1 <- gam(survival ~ s(age, bs="cc", k = 4) + 
            s(mother_id, bs="re") + s(litter_id, bs="re"),
          family=binomial, data=example, method = "ML")
summary(m1)
emmeans(m1, ~ s(age), type = "response", at = list(age = 1:6))
```

The code above provide the estimated probability of survival for 
integer values of age from 1 to 6. 

The question is if we can report the *mean* estimated probability 
of survival for all integer values from 2 to 5? 

In the manuscript, this can perhaps be reported like this:
_"The estimated probability of survival for pups of one year old mothers was 0.836 (95% CI: 0.779 - 0.880), 
for pups of mothers from two to five years ??? (95% CI: ...?), and for pups of mothers six years and older 
0.836 (95% CI: 0.779 - 0.880)."_

Note that ages six years and older are pooled together in the dataset.
